---
title: "Leaflet Assignment"
author: "John Paul Sanglay"
date: "January 16, 2019"
output: html_document
---

```{r setup,include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

## Introduction

The objective of the assignment is to create a webpage using R Markdown that features a map created with Leaflet.

The data used to create the interactive map comes from: https://en.wikipedia.org/wiki/List_of_cities_in_the_Philippines

The data references all of the cities in the Philippines and its corresponding population as of 2015.

## Map

There are a total of 145 citites in the Philippines with Quezon City having the highest population.


```{r,warning=FALSE}
library(leaflet)
df <- read.csv("phdat.csv")
colnames(df) <- c("name","pop","lat","lng")
map <- leaflet() %>%
        addTiles() %>%
        addMarkers(lng=df$lng, 
                   lat=df$lat,
                   popup=paste(df$name,"<br>Population: ",df$pop))%>%
        addCircles(lng=df$lng, 
                   lat=df$lat, 
                   weight=3, 
                   radius=sqrt(df$pop))
map
```